Parsing Postfix log files

### 2008-11-23 doc/logparser-acronyms.tex
Minor cleanups.

% % vim: set textwidth=75 spell :
% Note: every acronym is listed twice: once so it can be expanded, and once
% so it will appear with a long description in the glossary.
% Warning: do not use acronyms within definitions, they do not work
% properly.

@@

\newglossaryentry{SQL}{
    type=\acronymtype,
    name={SQL},
    description={Structured Query Language\glsadd{SQL glossary}}
}
\newglossaryentry{SQL glossary}{
    name={Structured Query Language},
    description={
        SQL is the standard language used for database querying,
        modification and maintenance.  Some information about SQL,
        including its history, can be found at
        \url{http://en.wikipedia.org/wiki/SQL}; a good introduction can be
        found at \url{http://philip.greenspun.com/sql/}.
    }
}

@@

\newglossaryentry{SLCT}{
    type=\acronymtype,
    name={SLCT},
    description={Simple Logfile Clustering Tool\glsadd{SLCT glossary}}
}
\newglossaryentry{SLCT glossary}{
    name={Simple Logfile Clustering Tool},
    description={
        SLCT~\cite{slct-paper} is a tool implementing an algorithm designed
        by Risto Vaarandi for identifying, grouping and producing a regex
        to match similar log lines.
    }
}

>>>>

% vim: set filetype=tex :
% Note: every acronym is listed twice: once so it can be expanded, and once
% so it will appear with a long description in the glossary.
% Warning: do not use acronyms within definitions, they do not work
% properly.

@@

\newglossaryentry{SQL}{
    type=\acronymtype,
    name={SQL},
    description={Structured Query Language\glsadd{SQL glossary}}
}
\newglossaryentry{SQL glossary}{
    name={Structured Query Language},
    description={
        The standard language used for database querying, modification, and
        maintenance.  Some information and history can be found at
        \url{http://en.wikipedia.org/wiki/SQL}; a good introduction can be
        found at \url{http://philip.greenspun.com/sql/}.
    }
}

@@

\newglossaryentry{SLCT}{
    type=\acronymtype,
    name={SLCT},
    description={Simple Logfile Clustering Tool\glsadd{SLCT glossary}}
}
\newglossaryentry{SLCT glossary}{
    name={Simple Logfile Clustering Tool},
    description={
        SLCT~\cite{slct-paper} is a tool implementing an algorithm designed
        by Risto Vaarandi for identifying, grouping, and producing a regex
        to match similar log lines.
    }
}

### 2008-11-23 doc/logparser-architecture.tex
Minor cleanups.

\label{why separate rules, actions and framework?}

@@

Decoupling the parsing rules from the associated actions and framework
allows new rules to be written and tested without requiring modifications
to the parser source code (significantly lowering the barrier to entry for
new or casual users who need to parse new log lines), and greatly
simplifies framework, actions and rules.  Decoupling also creates a clear
separation of functionality: rules handle low level details of identifying
log lines and extracting data from a log line; actions handle the higher
level details of following the path a mail takes through Postfix,
assembling the required data before storing it, dealing with complications
arising, etc; the framework provides services to actions and stores data.

@@

    \item Compare the results of parsing using sorted, shuffled and
        reversed rules (described in \sectionref{rule ordering for
        efficiency}).  Parse several log files using optimal ordering, then
        dump a textual representation of the rules, connections and results
        tables.  Repeat with shuffled and reversed ordering, starting with
        a fresh database.  If there are no overlapping rules the tables
        from each run will be identical; differences indicate overlapping
        rules.  The rules that overlap can be determined by examining the
        differences in the tables: each result contains a reference to the
        rule which created it, if the references differ between runs the
        two rules referenced in the differing results overlap.
        Unfortunately this method cannot prove the absence of overlapping
        rules; it can detect overlapping rules, but only if there are log
        lines in the input files that match more than one rule.

>>>>

\label{why separate rules, actions, and framework?}

@@

Decoupling the parsing rules from the associated actions and framework
allows new rules to be written and tested without requiring modifications
to the parser source code (significantly lowering the barrier to entry for
new or casual users who need to parse new log lines), and greatly
simplifies framework, actions, and rules.  Decoupling also creates a clear
separation of functionality: rules handle low level details of identifying
log lines and extracting data from a log line; actions handle the higher
level details of following the path a mail takes through Postfix,
assembling the required data before storing it, dealing with complications
arising, etc; the framework provides services to actions and stores data.

@@

    \item Compare the results of parsing using sorted, shuffled, and
        reversed rules (described in \sectionref{rule ordering for
        efficiency}).  Parse several log files using optimal ordering, then
        dump a textual representation of the rules, connections, and
        results tables.  Repeat with shuffled and reversed ordering,
        starting with a fresh database.  If there are no overlapping rules
        the tables from each run will be identical; differences indicate
        overlapping rules.  The rules that overlap can be determined by
        examining the differences in the tables: each result contains a
        reference to the rule which created it, if the references differ
        between runs the two rules referenced in the differing results
        overlap.  Unfortunately this method cannot prove the absence of
        overlapping rules; it can detect overlapping rules, but only if
        there are log lines in the input files that match more than one
        rule.

### 2008-11-23 doc/logparser-background.tex
Minor cleanups.

Postfix uses one restriction list (containing zero or more restrictions)
for each stage of the \gls{SMTP} conversation: client connection, HELO
command, MAIL FROM command, RCPT TO commands, DATA command, and end of
data.  The appropriate restriction list is evaluated for each stage
(evaluation will be explained shortly), though by default the restriction
lists for client connection, HELO and MAIL FROM commands will not be
evaluated until the first RCPT TO command is received, because some clients
do not deal properly with rejections before the first RCPT TO command; a
benefit of this delay is that Postfix has more information available when
logging rejections.

>>>>

Postfix uses one restriction list (containing zero or more restrictions)
for each stage of the \gls{SMTP} conversation: client connection, HELO
command, MAIL FROM command, RCPT TO commands, DATA command, and end of
data.  The appropriate restriction list is evaluated for each stage
(evaluation will be explained shortly), though by default the restriction
lists for client connection, HELO, and MAIL FROM commands will not be
evaluated until the first RCPT TO command is received, because some clients
do not deal properly with rejections before the first RCPT TO command; a
benefit of this delay is that Postfix has more information available when
logging rejections.

### 2008-11-23 doc/logparser-implementation.tex
Minor cleanups.

Please refer to \sectionref{parser design} for a discussion of why the
rules, actions and framework have been separated in the parser's design.
In this section algorithm can be taken to mean the combination of framework
and actions.

@@

A clear, comprehensible schema is essential when using the extracted data;
it is more important when using the data than when storing it, because
storing the data is a write-once operation, whereas utilising the data
requires frequent searching, sorting and manipulation of the data to
produce customised reports or statistics.

@@

    \item [result\_data] Sometimes rules need to save a result that is not
        present in the log line: e.g.\ setting \texttt{smtp\_code} when
        mail is accepted.  The format is: \newline{} \tab{} \texttt{XXX
        UPDATE EXAMPLE\@; smtp\_code = 550; \newline{} recipient = 2,
        sender = 4;} \newline{} i.e.\ semi-colon or comma separated
        assignment statements, with the variable name on the left and the
        value on the right hand side.\footnote{Commas and semi-colons
        cannot be escaped and thus cannot be used.  This feature is
        intended for use with small amounts of data rather than large
        amounts in any one rule, so dealing with escape sequences was
        deemed unnecessary.}  Any field in the results table can be set in
        this way; additionally \texttt{child} and \texttt{pid} are accepted
        and used respectively by the \texttt{TRACK}, \texttt{BOUNCE} and
        \texttt{SMTPD\_DIED} actions, but do not cause data to be entered
        in the database.

@@

Process scheduling can have a still more confusing effect: quite often the
child mail will be created, delivered and entirely finished with
\textbf{before} the parent logs the creation log line!  Thus, mails flagged
as coming from an unknown origin cannot be entered into the database when
their final log line is parsed; instead they must be marked as ready for
entry and subsequently entered once the parent mail has been identified.

@@

    \item [\daemon{local}, \daemon{pickup}, \daemon{smtp}:] Mail submitted
        locally \newline{} on the server, both local and remote delivery.

    \item [\daemon{local}, \daemon{smtp}, \daemon{smtpd}:] Mail accepted
        from a remote client, both local and remote delivery.

    \item [\daemon{local}, \daemon{smtpd}:] Mail accepted from a remote
        client, local delivery only.

    \item [\daemon{pickup}, \daemon{smtp}:] Mail submitted locally on the
        server, remote delivery only.

@@

    \item The hostname used in the HELO command is not logged if the mail
        is accepted.\footnote{Tested with Postfix 2.2.10, 2.3.11 and 2.4.7;
        this may possibly have changed in Postfix 2.5. XXX TEST THIS
        AGAIN.}  Rectifying this is relatively simple: create a restriction
        that is guaranteed to warn for every accepted mail, as follows:

@@

This section presented the core of the parser, starting with a very high
level view and the initial complications that arose.  A flow chart showing
the paths a mail may take through the nascent simplified algorithm was
provided, followed by an explanation of those paths, and a discussion of
the parser's emergent behaviour --- the data from the log files creates the
paths in the flow chart, they are not specified anywhere in the parser.
The framework which holds the parser together was covered next, after which
came a description of the current actions provided by the parser, and the
algorithm for analysing unparsed log lines to create regexes for new
rules.  Detecting, diagnosing and defeating complications forms the largest
single portion of this section, mirroring the development of the parser.
The complications are described in the order they were overcome, with
subsequent problems affecting fewer mails (often by an order or magnitude),
though the time required to solve problems increased with each successive
problem.

>>>>

Please refer to \sectionref{parser design} for a discussion of why the
rules, actions, and framework have been separated in the parser's design.
In this section algorithm can be taken to mean the combination of framework
and actions.

@@

A clear, comprehensible schema is essential when using the extracted data;
it is more important when using the data than when storing it, because
storing the data is a write-once operation, whereas utilising the data
requires frequent searching, sorting, and manipulation of the data to
produce customised reports or statistics.

@@

    \item [result\_data] Sometimes rules need to save a result that is not
        present in the log line: e.g.\ setting \texttt{smtp\_code} when
        mail is accepted.  The format is: \newline{} \tab{} \texttt{XXX
        UPDATE EXAMPLE\@; smtp\_code = 550; \newline{} recipient = 2,
        sender = 4;} \newline{} i.e.\ semi-colon or comma separated
        assignment statements, with the variable name on the left and the
        value on the right hand side.\footnote{Commas and semi-colons
        cannot be escaped and thus cannot be used.  This feature is
        intended for use with small amounts of data rather than large
        amounts in any one rule, so dealing with escape sequences was
        deemed unnecessary.}  Any field in the results table can be set in
        this way; additionally \texttt{child} and \texttt{pid} are accepted
        and used respectively by the \texttt{TRACK}, \texttt{BOUNCE}, and
        \texttt{SMTPD\_DIED} actions, but do not cause data to be entered
        in the database.

@@

Process scheduling can have a still more confusing effect: quite often the
child mail will be created, delivered, and entirely finished with
\textbf{before} the parent logs the creation log line!  Thus, mails flagged
as coming from an unknown origin cannot be entered into the database when
their final log line is parsed; instead they must be marked as ready for
entry and subsequently entered once the parent mail has been identified.

@@

    \item [\daemon{local}, \daemon{pickup}, \daemon{smtp}:] Mail submitted
        locally \newline{} on the server, for both local and remote
        delivery.

    \item [\daemon{local}, \daemon{smtp}, \daemon{smtpd}:] Mail accepted
        from a remote client, for both local and remote delivery.

    \item [\daemon{local}, \daemon{smtpd}:] Mail accepted from a remote
        client, for local delivery only.

    \item [\daemon{pickup}, \daemon{smtp}:] Mail submitted locally on the
        server, for remote delivery only.

@@

    \item The hostname used in the HELO command is not logged if the mail
        is accepted.\footnote{Tested with Postfix 2.2.10, 2.3.11, and 2.4.7;
        this may possibly have changed in Postfix 2.5. XXX TEST THIS
        AGAIN.}  Rectifying this is relatively simple: create a restriction
        that is guaranteed to warn for every accepted mail, as follows:

@@

This section presented the core of the parser, starting with a very high
level view and the initial complications that arose.  A flow chart showing
the paths a mail may take through the nascent simplified algorithm was
provided, followed by an explanation of those paths, and a discussion of
the parser's emergent behaviour --- the data from the log files creates the
paths in the flow chart, they are not specified anywhere in the parser.
The framework which holds the parser together was covered next, after which
came a description of the current actions provided by the parser, and the
algorithm for analysing unparsed log lines to create regexes for new
rules.  Detecting, diagnosing, and defeating complications forms the largest
single portion of this section, mirroring the development of the parser.
The complications are described in the order they were overcome, with
subsequent problems affecting fewer mails (often by an order or magnitude),
though the time required to solve problems increased with each successive
problem.

### 2008-11-23 doc/logparser-introduction.tex
Minor cleanups.

Section~\ref{background} provides background information useful in
understanding the thesis, parser, and architecture.  It introduces the idea
of using a database schema as an \gls{API}, providing an interface to the
data gathered that is language-neutral.  The novel separation of rules,
actions and framework is discussed, giving the reasons that approach was
taken when designing the parser.

@@

Section~\ref{conclusion} contains the conclusion of the thesis, describing
the results of the research, design and implementation of the parser.

>>>>

Section~\ref{background} provides background information useful in
understanding the thesis, parser, and architecture.  It introduces the idea
of using a database schema as an \gls{API}, to provide a language-neutral
interface to the data gathered.  The novel separation of rules, actions,
and framework is discussed, giving the reasons that approach was taken when
designing the parser.

@@

Section~\ref{conclusion} contains the conclusion of the thesis, describing
the results of the research, design, and implementation of the parser.

### 2008-11-23 doc/logparser-other-parsers-review.tex
Minor cleanups.

    \item Only \parsername{} makes it possible to parse new log lines
        without extensive and intrusive modifications to the parser;
        \parsername{}'s architecture is described in \sectionref{why
        separate rules, actions and framework?}.

@@

Berkeley DB only supports storing simple \textbf{(key, value)} pairs,
unlike \gls{SQL} databases that store arbitrary tuples.  In \gls{LMA}'s
main table the key is an integer referred to by secondary tables, and the
value is a \gls{CSV} line containing all of the data for that row.  The
secondary by-sender, by-recipient, by-date, and by-\gls{IP} tables use the
sender/recipient/date/\gls{IP} as the key, and the value is a \gls{CSV}
list of integers referring to the main table.  This effectively
re-implements \gls{SQL} foreign keys, but without the functionality offered
by even the most basic of \gls{SQL} databases (joins, ordering, searches,
etc.).  It also requires custom code to search on some combination of the
above, though the authors of \gls{LMA} did provide some queries: IP-STORY,
FROM-STORY, DAILY-EMAIL and DAILY-REJECT\@.  Berkeley DB appears to be the
least useful of the three output formats: it does not provide the
functionality of a basic \gls{SQL} database, not can it be used with
standard Unix text processing tools.

@@

\url{http://www.thesawmill.co.uk/formats/postfix.html} \newline{} Fields
extracted: from, to, server, UID, relay, status, number of recipients,
origin hostname, origin \gls{IP} and virus.  The fields \texttt{server},
\texttt{uid} and \texttt{virus} are not explained in the documentation:
\texttt{server} is probably the server the mail is delivered to, and
\texttt{uid} might be the uid of the user submitting mail locally.  Postfix
does not perform any form of virus checking (though it has many options for
cooperating with an external virus scanner), so the \texttt{virus} field is
a mystery.

\url{http://www.thesawmill.co.uk/formats/postfix_ii.html} \newline{} Fields
extracted: from, to, RBL, client hostname and client \gls{IP}\@.

\url{http://www.thesawmill.co.uk/formats/beta_postfix.html} \newline{}
Fields extracted: from, to, client hostname, client \gls{IP}, relay
hostname, relay \gls{IP}, status, response code, RBL and message id.

@@

YAALA uses a plugin based system to analyse log files and produce HTML
output reports, with all the parsing and report generation handled by
modules.  Using YAALA as a base would be only slightly less work than
starting from scratch, as both input and output modules would need to be
written specially; it may even be more work to implement the parser within
the constraints of YAALA\@.  YAALA supports storing previously gathered
data using Perl's Storable module~\cite{perl-storable}, so other Perl
programs can use Storable to load, examine, and optionally modify the data;
\parsername{} uses a well documented database which is accessible from the
majority of programming languages.  This information was gleaned from the
source code, as the documentation is sadly lacking.

>>>>

    \item Only \parsername{} makes it possible to parse new log lines
        without extensive and intrusive modifications to the parser;
        \parsername{}'s architecture is described in \sectionref{why
        separate rules, actions, and framework?}.

@@

Berkeley DB only supports storing simple \textbf{(key, value)} pairs,
unlike \gls{SQL} databases that store arbitrary tuples.  In \gls{LMA}'s
main table the key is an integer referred to by secondary tables, and the
value is a \gls{CSV} line containing all of the data for that row.  The
secondary by-sender, by-recipient, by-date, and by-\gls{IP} tables use the
sender/recipient/date/\gls{IP} as the key, and the value is a \gls{CSV}
list of integers referring to the main table.  This effectively
re-implements \gls{SQL} foreign keys, but without the functionality offered
by even the most basic of \gls{SQL} databases (joins, ordering, searches,
etc.).  It also requires custom code to search on some combination of the
above, though the authors of \gls{LMA} did provide some queries: IP-STORY,
FROM-STORY, DAILY-EMAIL, and DAILY-REJECT\@.  Berkeley DB appears to be the
least useful of the three output formats: it does not provide the
functionality of a basic \gls{SQL} database, not can it be used with
standard Unix text processing tools.

@@

\url{http://www.thesawmill.co.uk/formats/postfix.html} \newline{} Fields
extracted: from, to, server, UID, relay, status, number of recipients,
origin hostname, origin \gls{IP}, and virus.  The fields \texttt{server},
\texttt{uid} and \texttt{virus} are not explained in the documentation:
\texttt{server} is probably the server the mail is delivered to, and
\texttt{uid} might be the uid of the user submitting mail locally.  Postfix
does not perform any form of virus checking (though it has many options for
cooperating with an external virus scanner), so the \texttt{virus} field is
a mystery.

\url{http://www.thesawmill.co.uk/formats/postfix_ii.html} \newline{} Fields
extracted: from, to, RBL, client hostname, and client \gls{IP}\@.

\url{http://www.thesawmill.co.uk/formats/beta_postfix.html} \newline{}
Fields extracted: from, to, client hostname, client \gls{IP}, relay
hostname, relay \gls{IP}, status, response code, RBL, and message id.

@@

YAALA uses a plugin based system to analyse log files and produce HTML
output reports, with all the parsing and report generation handled by
modules.  Using YAALA as a base would be only slightly less work than
starting from scratch, as both the input and output modules would need to
be written specially; it may even be more work to implement the parser
within the constraints of YAALA\@.  YAALA supports storing previously
gathered data using Perl's Storable module~\cite{perl-storable}, so other
Perl programs can use Storable to load, examine, and optionally modify the
data; \parsername{} uses a well documented database which is accessible
from the majority of programming languages.  This information was gleaned
from the source code, as the documentation is sadly lacking.

### 2008-11-23 doc/logparser-postfix-daemons.tex
Minor cleanups.

\newglossaryentry{virtual}{name={virtual},type={postfix},description={
    Virtual is the Postfix component responsible for delivery of mails to
    virtual domains.  With \daemon{local} delivery the destination is
    determined only by the portion of the email address on the left side of
    the \at{}, whereas with \daemon{virtual} delivery the destination is
    determined by the entire email address, e.g.\ if the server considers
    itself responsible for both \textbf{example.org} and
    \textbf{example.net} domains: \daemon{local} considers
    \textbf{john\at{}example.org} and \textbf{john\at{}example.net} to have
    the same mailbox, whereas \daemon{virtual} considers them to have
    different mailboxes.  Virtual delivery is used when a server hosts
    multiple domains where a username may be present in more than one
    domain but represent different users in each.  The definitive
    documentation is
    \url{http://www.postfix.org/virtual.8.html}.
}}

>>>>

\newglossaryentry{virtual}{name={virtual},type={postfix},description={
    Virtual is the Postfix component responsible for delivery of mails to
    virtual domains.  With \daemon{local} delivery the destination is
    determined only by the portion of the email address on the left side of
    the \at{}, whereas with \daemon{virtual} delivery the destination is
    determined by the entire email address.  E.g.\ if the server is
    responsible for both the \textbf{example.org} and \textbf{example.net}
    domains: \daemon{local} considers \textbf{john\at{}example.org} and
    \textbf{john\at{}example.net} to have the same mailbox, whereas
    \daemon{virtual} considers them to have different mailboxes.  Virtual
    delivery is used when a server hosts multiple domains where a username
    may be present in more than one domain but represent different users in
    each.  The definitive documentation is
    \url{http://www.postfix.org/virtual.8.html}.
}}

### 2008-11-23 doc/logparser-results.tex
Minor cleanups.

How any architecture scales as the number of rules increases is important,
but it is particularly important in this architecture because it is
expected that the typical parser will have a large number of rules.  There
are \numberOFrules{} rules in the full Postfix ruleset, whereas the minimum
number of rules required to parse the \numberOFlogFILES{} log files used
when generating the results in this thesis is \numberOFrulesMINIMUM{},
\numberOFrulesMINIMUMpercentage{} of the full ruleset.  The full ruleset is
larger because the Postfix parser is tested with \numberOFlogFILESall{} log
files, to improve its parsing and ensure it correctly parses logs generated
by later Postfix versions.  A second set of statistics was generated using
the minimum ruleset and compared to the statistics generated using the full
ruleset: the percentage parsing time increase when using the full ruleset
instead of the minimal ruleset for optimal, shuffled and reversed orderings
is shown in \graphref{Percentage parsing time increase of maximum ruleset
over minimum ruleset}.

@@

    \item Every effort has been made while developing to make the parser as
        precise, demanding and particular as possible.

@@

Parser coverage is divided into two topics in this section: log lines
covered and mails covered.  The former is initially more important, as the
parser must successfully parse every line if it is to be complete, but
subsequently the latter takes precedence because reproducing the path a
mail takes through Postfix is the aim of the parser.  Increasing the
percentage of log lines parsed is relatively simple and non-intrusive:
adding new rules or modifying existing rules is simplified by the
separation of rules, actions and framework.  Improving the logical coverage
is harder, as the actions taken by Postfix must be reconstructed by the
author, and the new sequence of actions integrated into the existing model
without breaking the existing parsing.  Detecting a deficiency in the
parsing algorithm is also significantly harder than detecting unparsed log
lines, as the parser will warn about any unparsed line, whereas discovering
a flaw in the parser requires understanding of the warnings produced and
the mails remaining in the state table.  Rectifying a flaw in the parser
requires an understanding of both the parser and Postfix's log files, and
investigative work to determine the cause of the deficiency, followed by
further examination of the log files in developing a solution.

>>>>

How any architecture scales as the number of rules increases is important,
but it is particularly important in this architecture because it is
expected that the typical parser will have a large number of rules.  There
are \numberOFrules{} rules in the full Postfix ruleset, whereas the minimum
number of rules required to parse the \numberOFlogFILES{} log files used
when generating the results in this thesis is \numberOFrulesMINIMUM{},
\numberOFrulesMINIMUMpercentage{} of the full ruleset.  The full ruleset is
larger because the Postfix parser is tested with \numberOFlogFILESall{} log
files, to improve its parsing and ensure it correctly parses logs generated
by later Postfix versions.  A second set of statistics was generated using
the minimum ruleset and compared to the statistics generated using the full
ruleset: the percentage parsing time increase when using the full ruleset
instead of the minimal ruleset for optimal, shuffled, and reversed
orderings is shown in \graphref{Percentage parsing time increase of maximum
ruleset over minimum ruleset}.

@@

    \item Every effort has been made while developing to make the parser as
        precise, demanding, and particular as possible.

@@

Parser coverage is divided into two topics in this section: log lines
covered and mails covered.  The former is initially more important, as the
parser must successfully parse every line if it is to be complete, but
subsequently the latter takes precedence because reproducing the path a
mail takes through Postfix is the aim of the parser.  Increasing the
percentage of log lines parsed is relatively simple and non-intrusive:
adding new rules or modifying existing rules is simplified by the
separation of rules, actions, and framework.  Improving the logical coverage
is harder, as the actions taken by Postfix must be reconstructed by the
author, and the new sequence of actions integrated into the existing model
without breaking the existing parsing.  Detecting a deficiency in the
parsing algorithm is also significantly harder than detecting unparsed log
lines, as the parser will warn about any unparsed line, whereas discovering
a flaw in the parser requires understanding of the warnings produced and
the mails remaining in the state table.  Rectifying a flaw in the parser
requires an understanding of both the parser and Postfix's log files, and
investigative work to determine the cause of the deficiency, followed by
further examination of the log files in developing a solution.
